---
title: "DATA607_Homework2"
output: html_document 
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Load packages to connect to MySQL database
```{r}
install.packages("RMySQL", repos = "http://cran.us.r-project.org")
install.packages("Rtools", repos = "http://cran.us.r-project.org")
library(DBI)
library(RMariaDB)
library(ggplot2)
```


Connect to MySQL database
```{r}
source("login_credentials.R")
mydb = dbConnect(RMariaDB::MariaDB(), user=username, password=password, dbname='movie',host='localhost')
```


Query movies table from SQL
```{r}
dbGetQuery(mydb,'SELECT *
           FROM movie.movie_review
           ORDER BY review_id') 
```


Load results from query to dataframe 
```{r}
movie_review_results <- dbGetQuery(mydb, 'SELECT * 
            FROM movie.movie_review
            ORDER BY review_id')

movie_review_results
```


Testing visualizations using ggplot
```{r}
ggplot(movie_review_results, aes(x = rating)) + geom_bar()
```


Bar graph with labels
```{r}
ggplot(movie_review_results, aes(x = rating)) + theme_bw() + geom_bar() + labs(y = "Rating Count", x = "Rating", title = "Overall Rating Totals")
```


Adding some color to the graph to assist with the data visualization
```{r}
ggplot(movie_review_results, aes(x = rating, fill = movie_name)) + theme_bw() + geom_bar() + labs(y = "Rating Count", x = "Rating", title = "Overall Ratings")
```


Grouping ratings based on reviewer ID. 
```{r}
ggplot(movie_review_results, aes(x = rating, fill = movie_name)) + theme_bw() + facet_wrap(~ reviewer_id) + geom_bar() + labs(y = "Rating Count", x = "Rating", title = "Ratings Grouped by Reviewer ID")
```


Grouping ratings based on reviewer first name. 
```{r}
ggplot(movie_review_results, aes(x = rating, fill = movie_name)) + theme_bw() + facet_wrap(~ first_name) + geom_bar() + labs(y = "Rating Count", x = "Rating", title = "Ratings Grouped by Reviewer Name")
```


Plaing with boxplot for the same ratings but I prefer the colored bar graph
```{r}
ggplot(movie_review_results, aes(x = movie_name, y = rating)) + theme_bw() + geom_boxplot() + labs(y = "Movie Rating", x = "Movie Name", title = "Movie Ratings")
```


